A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-10 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
CWP CSBS: address comments about algorithms in 3.3

Seven key areas, itemised below, have been identified where research and
development is necessary to enable the community to exploit the full
power of the enormous datasets that we will be collecting. Three of
these areas concern the increasingly parallel and heterogeneous
computing architectures that we will have to write our code for. In
addition to a general effort to vectorise our codebases, we must
understand what kinds of algorithms are best suited to what kinds of
hardware architectures, develop benchmarks that allow us to compare the
physics-per-dollar-per-watt performance of different algorithms across a
range of potential architectures, and find ways to optimally utilise
heterogeneous processing centres. The consequent increase in the
complexity and diversity of our codebase will necessitate both a
determined push to educate physicists in modern coding
practices, and a development of more sophisticated and automated quality
assurance and control. The increasing granularity of
our detectors, and the addition of timing information, which seems
mandatory to cope with the extreme pileup conditions at the HL-LHC, will
require new kinds of reconstruction algorithms that are sufficiently
fast for use in real-time. Finally, the increased
signal rates will mandate a push towards real-time analysis in many
areas of HEP, in particular those with low-p\textbf{\textsubscript{T}}
signatures.

>>>>

Seven key areas, itemised below, have been identified where research and
development is necessary to enable the community to exploit the full
power of the enormous datasets that we will be collecting. Three of
these areas concern the increasingly parallel and heterogeneous
computing architectures that we will have to write our code for. In
addition to a general effort to vectorise our codebases, we must
understand what kinds of algorithms are best suited to what kinds of
hardware architectures. It is an area where collaboration with the
computer science community is required. We also need to develop
benchmarks that allow us to compare the
physics-per-dollar-per-watt performance of different algorithms across a
range of potential architectures, and find ways to optimally utilise
heterogeneous processing centres. The consequent increase in the
complexity and diversity of our codebase will necessitate both a
determined push to educate physicists in modern algorithmic approaches and coding practices,
and a development of more sophisticated and automated quality
assurance and control. The increasing granularity of
our detectors, and the addition of timing information, which seems
mandatory to cope with the extreme pileup conditions at the HL-LHC, will
require new kinds of reconstruction algorithms that are sufficiently
fast for use in real-time. Finally, the increased
signal rates will mandate a push towards real-time analysis in many
areas of HEP, in particular those with low-p\textbf{\textsubscript{T}}
signatures.
